Laser Ranger
========================================================

The laser ranger used in the UltraPilot takes advantage of the parallax effect
in order to measure the distance to objects in front of the sensor. A laser and
camera are set up in a rig pointing in exactly the same direction.

In the examples shown here, the following setup is assumed:
* Raspberry Pi camera (53° field of view, 2592 pixels across)
* Laser pointer reflecting on a wavelength that can be read by the camera
* A rig holding both with their centers 55 mm apart

Because the distance between the centers of both the camera and the laser
pointer are known, and the angle between the camer's center and the laser can be
determined by the pixel position of the detected laser reflection, a simple
trigonometric calculation can be used to calculate the distance between the
laser and the object it strikes:

```{r eval=FALSE, echo=TRUE}
# rig.length - Distance between centers of camera and laser
# angle - Degrees from directly in front of camera and detected laser reflection
distance <- function(rig.length, angle) {
  require(aspace)
  rig.length * tan(as_radians(90) - as_radians(angle))
}
```

For the Raspberry Pi's camera, this would produce the following precision:

```{r fig.width=7, fig.height=6}
# lit.pixel - Pixel lit by laser, on x-axis from left- (0) to rightmost
# rig.length - Distance between centers of camera and laser in mm
# picture.width - Picture width in pixels
# fov - Camera's field of view in degrees
distance.rpi <- function(lit.pixel, rig.length=55, picture.width=2592, fov=53) {
  require(aspace)
  picture.middle <- picture.width / 2
  radians.per.pixel <- as_radians(fov) / picture.width
  if (lit.pixel < picture.middle) stop("Instrument error.")
  angle <- radians.per.pixel * (lit.pixel - picture.middle)
  rig.length * tan(as_radians(90) - angle)
}
options(scipen=20)
picture.width <- 2595
plot(distance.rpi((picture.width / 2):picture.width),
     main="Distance per pixel, entire range",
     ylab="Distance (mm)",
     xlab="Pixels from center")
# It is readily apparent that the sensor's precision is extremely low at high
# distances. If we plot a shorter range, though, we see that the precision is
# relatively high - at least in theory.
plot(distance.rpi((picture.width / 2):((picture.width / 2) + 70)) / 10,
     main="Distance per pixel, relevant range",
     ylab="Distance (cm)",
     xlab="Pixels from center")
# If we examine the sensor's performance at different ranges, the results are
# quite promising.
distances <- distance.rpi((picture.width / 2):picture.width) / 10
differences <- abs(diff(distances))
plot(distances, c(differences, 0),
     main="Resolution at varying ranges",
     ylab="cm",
     xlab="Range (cm)")
# Especially the target range from 0-400 cm is promising.
distances <- distances[distances < 400]
differences <- abs(diff(distances))
plot(distances, c(differences, 0),
     main="Resolution at varying ranges",
     ylab="cm",
     xlab="Range (cm)")
# Even at a range of 400 cm, the device's precision is very high (under 10cm):
differences[1]

# Practically speaking, probably more than one pixel will be lit by the laser,
# so this precision will decrease.
```
